---
title: "graphs"
author: "Biandri Joubert"
date: '2022-07-15'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)


library(readxl)
library(tidyverse)
library(openxlsx)
library(flextable)
library(writexl)

```

## Analysing student marks with the help of R

```{r, echo=FALSE}
student_results<-read_excel("/Users/biandrijoubert/Google Drive/R_Projects/website_why_R/content/topic_2/graph_examples_1/student_results.xlsx")

list_of_names <- unique(student_results$Name)


```

_**The following students attended this course:**_ `r paste0(list_of_names)`.

For a student to qualify to sit for examination they are required to fulfill the following:
- At least 50% class attendance.   
- An average of 60 % across the assessments. The lowest mark falls away and the average is taken across the remaining results, including the bonus marks that are awarded during unplanned assessments in class.  
- Class attendance of more that 70% can justify an additional 2% to the students average should they require it for qualification to sit for examination. 

The course was assessed in the following manner: 
- Three tests. Test one - 100 marks, test two - 50 marks, test three 100 marks. The best two out of three count towards the semester mark. 



